Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-03-07 src/article.tex
Revise results section

The Scaffolder software allows computational joining of nucleotide sequences
together into a single contiguous scaffolded super-sequence. Plain-text
scaffold files written in the YAML syntax specify how these sequences should be
joined and the scaffolder software is used to generate the scaffold sequence.
In addition to specifying which contigs are required, the scaffold file allows
the contigs to be edited into smaller sub-sequences or reverse complemented if
necessary. The process of genome finishing may involve producing additional
oligonucleotide sequences to fill unknown regions in the scaffold. The scaffold
file format allows these additional insert sequences to bridge gaps. These
inserts can also be treated in a similar way to larger contig sequences:
trimmed and/or reverse complemented to match the corresponding gap region. \pb

The distances between contigs may be estimated from paired-read data or from
mapping the contigs to a reference genome. These inter-contig gap regions are
useful to join separate sequences together by an estimated size and the
scaffold file allows for the specification of such unresolved regions. The use
of these regions in the scaffold indicates the unresolved regions in the build
and their approximate size. \pb

The scaffold file specifies how sequence regions are joined together; however
the sequences themselves are not stored in the scaffold file and are instead
maintained as a separate FASTA file. Nucleotide sequences in a FASTA-formatted
file are the standard output for a genome assembler, and these may be contigs,
sets of contigs scaffolded into larger sequences, or both. These nucleotide
sequences stored in the FASTA file are referenced in the scaffold using the
first word from in the FASTA header of the corresponding sequence. Maintaining
the nucleotide sequences in a separate file preserves the unedited sequence and
decouples the data from the scaffold file describing how it should be used to
in the genome sequence. \pb

@@

The final entry in the scaffold also includes the ``inserts'' tag to add
additional regions of sequence. These inserts are also added as a YAML list,
with each insert beginning with a dash. The first insert, shown in purple,
similar attributes to that of a sequence entry; the reverse, start and stop
tags are used to trim and reverse complement the insert. Similarly the `source'
tag identifies the corresponding FASTA sequence as `insert1'. The ``open'' and
``close'' tags are specific to inserts and determine where the insert is added
in the enclosing sequence. The region of the sequence inside these coordinates
is inclusively replaced by the specified insert sequence. This is visualised in
the putative gene Figure 1 by the black lines bisecting the blue sequence. \pb

The next insert, shown in brown, is specified using only the `open' tag. This
illustrates that only one of either `open' or `close' tags is required when
adding an insert sequence. If only one of the `open' or `close' tags is used
the corresponding opposing position distance is calculated from the length of
the insert FASTA sequence. This allows inserts to bridge into, and partially
fill gap regions without requiring an end coordinate position. \pb

>>>>

The Scaffolder software allows computational joining of nucleotide sequences
together into a single contiguous scaffolded super-sequence. Plain-text
scaffold files written in the YAML syntax specify how these sequences should be
joined and the scaffolder software is used to generate the scaffold sequence.
In addition to specifying which contigs are required, the scaffold file allows
the contigs to be edited into smaller sub-sequences or reverse complemented if
necessary. The process of genome finishing may involve producing additional
oligonucleotide sequences to fill unknown regions in the scaffold and The
scaffold file format allows these additional insert sequences to bridge gaps.
These inserts can also be treated in the same manner as larger contig
sequences: trimmed and/or reverse complemented to match the corresponding gap
region. \pb

The distances between contigs may be estimated from paired-read data or from
mapping the contigs to a reference genome. These inter-contig gap regions are
useful to join separate sequences together by an estimated size and the
scaffold file allows for the specification of such unresolved regions by
inserting regions of `N' nucleotides into the scaffold. The use of these
regions in the scaffold indicates the unresolved regions in the build and their
approximate size. \pb

The scaffold file specifies how sequence regions are joined together; however
the sequences themselves are not stored in the scaffold file and are instead
maintained as a separate FASTA file. Nucleotide sequences in a FASTA-format
file are the standard output for a genome assembler, and these may be contigs,
sets of contigs scaffolded into larger sequences, or both. These nucleotide
sequences stored in the FASTA file are referenced in the scaffold using the
first word from in the FASTA header of the corresponding sequence. Maintaining
the nucleotide sequences in a separate file preserves the unedited sequence and
decouples the data from the scaffold file describing how it should be used to
in the genome sequence. \pb

@@

The final entry in the scaffold also includes the ``inserts'' tag to add
additional regions of sequence. These inserts are also added as a YAML list,
with each insert beginning with a dash. The first insert, shown in purple,
similar attributes to that of a sequence entry; the reverse, start and stop
tags are used to trim and reverse complement the insert. Similarly the `source'
tag identifies the corresponding FASTA sequence as `insert1'. The ``open'' and
``close'' tags are specific to inserts and determine where the insert is added
in the enclosing sequence. The region of the sequence inside these coordinates
is inclusively replaced by the specified insert sequence. This is visualised in
the putative genome in Figure 1 by the black lines bisecting the blue sequence.
\pb

The next insert, shown in brown, is specified using only the `open' tag. This
illustrates that only one of either `open' or `close' tags is required when
adding an insert sequence. If only one of the `open' or `close' tags is used
the corresponding opposing `open'/`close' coordinate is calculated from the
length of the insert FASTA sequence. This allows inserts to bridge into, and
partially fill gap regions, without requiring an end coordinate position. \pb
